Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
added some sections to the latex, made some small changes to current sections

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

@@

\begin{abstract}
In this paper we compare Recurrent Neural Network (RNN)
approximations of language models to traditional n-gram based models.
We evaluate different recurrent model architectures, hyperparameter configurations,
encoder and decode configurations and regularization and intialization procedures
and compare their performance on various performance and natural language
generation metrics. We find that in general, Long Short-Term Memory models
with embedding layers at the encoder stage outperforms other models
in terms of inference metrics and computational performance.
\end{abstract}

@@

Since the publication of \cite{Milkolov10}, new RNN approaches have shown
improvement on the state-of-the-art. We examine these new architectures and
techniques for future work discussed in the Milkolov paper and analyze whether their
results indicate that improvements can be made on the baseline set by the paper.

@@

$$ WER = \frac{S + D + I}{N} $$, where $N$ is the number of
words and $S, D, I$ are substituions, deletions, insertions.

@@

@@

The RNN is trained via "back-propagation through time" (BPTT), which is
effectively the same as the back-propgation algorithm proposed for feed-forward
neural networks, but applied to the recurrent structure of the RNN. In effect,
BPTT involves the same application of the chain rule to recurrent function
applications, and hidden layer states, but usually with some sort of threshold
to prevent computational complexity scaling with the number of tokens the
network has seen so far. In practice this means that the hidden layer encodes
a context window \emph{up to} to a certain length, but no longer than
that length.

\subsection{LSTM}
\label{sec:lstm}

\subsection{GRU}
\label{sec:gru}

@@

\subsection{Embeddings}
\label{sec:embedddings}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\graphicspath{ {./images/} }

@@

\begin{abstract}
In this paper we compare Recurrent Neural Network (RNN)
approximations of language models to traditional n-gram based models.
We evaluate different recurrent model architectures, hyperparameter configurations,
encoder and decoder configurations and regularization and intialization procedures
while comparing their performance on various performance and natural language
generation metrics. We find that in general, Long Short-Term Memory models
with embedding layers at the encoder stage outperforms other models
in terms of inference metrics and computational performance.
\end{abstract}

@@

One of the first papers applying RNNs to Language Modeling was \cite{Milkolov10}. But since 2010, new RNN approaches have shown
improvement on the state-of-the-art. We examine these new architectures and
techniques for future work discussed in the Milkolov paper and analyze whether their
results indicate that improvements can be made on the baseline set by the paper.

@@

$$ WER = \frac{S + D + I}{N} $$, where $N$ is the number of
words and $S, D, I$ are substitutions, deletions, insertions.

@@

\subsection{METEOR}
\label{sec:meteor}
Another metric trying to improve BLEU is METEOR. The novel thing about this metric is the use of Recall as well as Precision to compute the score. It computes the harmonic mean of Recall and Precision over uni-grams, the weight for recall being higher than Precision, meaning that false negatives (having a low probability for the true word trying to predict) will have a big impact on the metric (the score will be lower as the amount of false negatives increase).

More formally, Precision over an uni-gram is computed as:
$$P={\frac  {m}{w_{{t}}}}$$
Where m is the number of uni-grams in the candidate translation that are also found in the reference translation, and $w_t$ is the number of uni-grams in the candidate translation.

Recall is computed as:
$$R={\frac  {m}{w_{{r}}}}$$
Where m is as above, and $w_{{r}}$ is the number of uni-grams in the reference translation. Precision and recall are combined using the harmonic mean in the following fashion, with recall weighted 9 times more than precision:
$$F_{{mean}}={\frac  {10PR}{R+9P}}$$

@@

The RNN is trained via "back-propagation through time" (BPTT), which is
effectively the same as the back-propagation algorithm proposed for feed-forward
neural networks, but applied to the recurrent structure of the RNN. In effect,
BPTT involves the same application of the chain rule to recurrent function
applications, and hidden layer states, but usually with some sort of threshold
to prevent computational complexity scaling with the number of tokens the
network has seen so far. In practice this means that the hidden layer encodes
a context window \emph{up to} to a certain length, but no longer than
that length.

\subsection{LSTM}
\label{sec:lstm}
The LSTM cell builds upon the basic RNN cell and adds some gates in order to control how information is stored or deleted. These gates are element-wise operations, meaning that every value of the hidden state have a dedicated gate deciding the fate of that value in the next time step. All the gates are computed taking on account the last hidden state and the new input and they are applied onto the last hidden state.

The first gate applied is a "forget" gate that regulates how much of the last hidden state is conserved in this time step. 
The second one is a "storing" gate that decides how much of the new input is encoded into the hidden state.
The last gate is an "output" gate which decides which parts of the hidden state are taken on account to compute the output. This output will pass through a softmax layer to get the prediction for that time step.

Thanks to this procedure, hidden units can be ignored by the output gate and they can propagate forward in time without being multiplied by a weight matrix and applied an activation function at every time step, helping overcome the gradient vanishing problem.

The forgetting and storing gates help encoding only relevant information into the hidden state, improving long-time dependencies recall.
\subsection{GRU}
\label{sec:gru}
GRU is a simplified LSTM cell in which the forget and store gates are combined into one "update" gate with complementary gated values (they sum up to 1 for every hidden unit), this means that the hidden state will "forget" some information only if it is going to learn some new information.

@@

\subsection{Embeddings}
\label{sec:embedddings}
Traditionally, the Language Models were feeded each word as a One-Hot encoded vector as large as the vocabulary is. Since vocabularies can be really large (20k to 800k for languages with many compounded words such as Finnish), this presents a computational problem, large matrices multiplication is expensive.
Word Embeddings provide an alternative procedure in which the words to be feeded to the network are encoded in an $n$ dimensional space. The embedding layer can learn a word encoding such that words related to each other semanticaly, get similar encoded vectors after the transformation.
Even some basic arithmetic is possible. For example, if you subtract the vector for "queen" from the vector for "king" you get the vector for "man".

\includegraphics[width=\textwidth]{01}
